The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-20 dit-paper_ieee.tex
Explained the period range as requested in issue #21

	We thus checked the existence condition on 10000 systems generated by:
	\begin{itemize}
		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with parameters:
		\begin{itemize}
			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
			\item $n$ (number of tasks) set to several values (see Fig.~\ref{fig:noFPDIT})
		\end{itemize}
		\item Choosing the $T_i$ uniformly between 5 and 20, which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
		\item Choosing the $D_i$ uniformly in the interval $[T_i - CDF(T_i - C_i), T_i]$, where $CDF$ varies between 0 and 1 and is called the \emph{Constrained Deadline Factor}. It allows us to generate systems where the deadlines are closer to the period.
	\end{itemize}

@@

	In Fig.~\ref{fig:sizeRatio} a number of feasible asynchronous task sets of
	three tasks without synchronous instants were generated. The size of their
	C-space (number of valid WCET vectors) was compared with that of the same
	task sets with all offsets set to zero. The systems were generated as in section~\ref{sct:noFPDITsimu}
	and the integer linear problems used to remove redundancies were solved via the GLPK tool\footnote{\url{http://www.gnu.org/software/glpk/}}.

>>>>

	We thus checked the existence condition on 10000 systems generated by:
	\begin{itemize}
		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with parameters:
		\begin{itemize}
			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
			\item $n$ (number of tasks) set to several values (see Fig.~\ref{fig:noFPDIT})
		\end{itemize}
		\item Choosing the $T_i$ uniformly between 5 and 20 (in order to have a manageable value of $H$), which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
		\item Choosing the $D_i$ uniformly in the interval $[T_i - CDF(T_i - C_i), T_i]$, where $CDF$ varies between 0 and 1 and is called the \emph{Constrained Deadline Factor}. It allows us to generate systems where the deadlines are closer to the period.
	\end{itemize}

@@

	In Fig.~\ref{fig:sizeRatio} a number of feasible asynchronous task sets of
	three tasks without synchronous instants were generated as described in Section~\ref{sct:noFPDITsimu}. The size of their
	C-space (number of valid WCET vectors) was compared with that of the same
	task sets with all offsets set to zero. The systems were generated as in section~\ref{sct:noFPDITsimu}
	and the integer linear problems used to remove redundancies were solved via the GLPK tool\footnote{\url{http://www.gnu.org/software/glpk/}}.
